\dppTitle

### 2014-06-02 manuscripts/dpp-msbayes/cover-letter/cover-letter.tex
Updating dpp ms cover letter for re-submission.

\documentclass[letterpaper,11pt]{letter}
\usepackage{anysize}
\marginsize{0.8in}{0.8in}{-0.2in}{0.3in}
\usepackage{setspace}
\usepackage{url}
\usepackage{verbatim}
\usepackage{parskip}
\usepackage{xspace}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue}

@@

\signature{Jamie Oaks, Postdoctoral Fellow \\ 
                 Department of Biology \\
                 University of Washington \\ 
                 % Box 351800 \\ 
                 Seattle, WA 98195, USA \\
                 \href{mailto:joaks1@uw.edu}{\texttt{joaks1@uw.edu}} \\ 
                 \href{http://www.phyletica.com}{\texttt{www.phyletica.com}}}
\begin{document}
\begin{letter}{\emph{BMC Evolutionary Biology} \\
                        BioMed Central \\
                        236 Gray's Inn Road \\
                        London WC1X 8HB \\
                        United Kingdom}
\opening{Dear Editor:}
% \raggedright
I am submitting a manuscript entitled ``An Improved Approximate-Bayesian
Model-choice Method for Estimating Shared Evolutionary History'' to be
considered for publication in \emph{BMC Evolutionary Biology}.
This is a methodological article, and the field of research is comparative
biogeography and Bayesian model choice.

@@

Thank you for your consideration, and I look forward to your correspondence
regarding this manuscript.

>>>>

\documentclass[letterpaper,11pt]{letter}
\usepackage{anysize}
\marginsize{0.6in}{0.6in}{-0.4in}{0.3in}
\usepackage{setspace}
\usepackage{url}
\usepackage{verbatim}
\usepackage{parskip}
\usepackage{xspace}
\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0}, colorlinks=true, urlcolor=blue}

@@

\signature{Jamie Oaks, Postdoctoral Fellow \\ 
                 Department of Biology \\
                 University of Washington \\ 
                 % Box 351800 \\ 
                 Seattle, WA 98195, USA \\
                 \href{mailto:joaks1@uw.edu}{\texttt{joaks1@uw.edu}} \\ 
                 \href{http://www.phyletica.com}{\texttt{www.phyletica.com}}}
\begin{document}
\begin{letter}{\emph{BMC Evolutionary Biology} \\
                        BioMed Central \\
                        236 Gray's Inn Road \\
                        London WC1X 8HB \\
                        United Kingdom}
\opening{Dear Editor:}
% \raggedright
I am re-submitting a manuscript entitled ``An Improved Approximate-Bayesian
Model-choice Method for Estimating Shared Evolutionary History'' to be
considered for publication in \emph{BMC Evolutionary Biology}.
The manuscript ID of the previous submission was 9419461361233299.
This is a methodological article, and the field of research is comparative
biogeography and Bayesian model choice.

@@

The previous submission of this manuscript was handled by Editor Dr.\  Peter
G.\ Foster, who obtained two anonymous reviews.
I have incorporated the revisions recommended by Dr.\ Foster and the reviewers.
My point-by-point response to reviewer comments follows this letter.
Thank you for your consideration, and I look forward to your correspondence
regarding this manuscript.
